\input{include.tex}

\begin{document}
\pagestyle{empty}

\CardTitle{Elara}

\begin{tabular}{p{0.3\linewidth}p{0.3\linewidth}p{0.1\linewidth}p{0.3\linewidth}}
\head{Attack}        & \head{Range}         & \head{Hit}     & \head{Damage}   \\
Dagger               & 5 feet (melee)       & +5             & 1d4+3 Piercing  \\
Dagger               & 20/60 feet (thrown)  & +5             & 1d4+3 Piercing  \\
Shortbow             & 80 feet              & +5             & 1d6+3 Piercing  \\
\m{Starry Wisp}      & 60 feet              & +4             & 1d8 Radiant     \\
\m{Vicious Mockery}  & 60ft                 & WIS 12         & 1d6 Psychic
\end{tabular}

{\rule{\linewidth}{0.4pt}}
\vspace{1em}

\begin{tabular}{p{0.3\linewidth}p{0.3\linewidth}p{0.4\linewidth}}
\multicolumn{2}{l}{\head{Actions}} & \head{Bonus Actions} \\
  Dash                                                 & Improvise                & Bardic Inspiration \freq{2/long rest} \\
  Disengage                                            & Influence                & \m[1]{Healing Word} \\
  \m[1]{Dissonant Whispers}                            & \m{Light}                & \\
  Dodge                                                & \m{Minor Illusion}       & \head{Reactions} \\
  \m[1]{Faerie Fire}                                   & Magic                    & Opportunity Attack \\
  \m{Guidance}                                         & Ready                    & \\
  Grapple                                              & Search                   & \\
  Help                                                 & Shove                    & \\
  \m{Healing Hands} \freq{1/long rest}                 & \multicolumn{2}{l}{\m[1]{Speak with Animals} \freq{1/long rest}}  \\
  Hide                                                 & Study &
\end{tabular}

\newpage
\CardTitle{Elara}

\begin{tabular}{r@{\hspace{0.5em}}c@{\hspace{0.5em}}c@{\hspace{0.5em}}c@{\hspace{0.5em}}c@{\hspace{0.5em}}c@{\hspace{0.5em}}c}
                  & \head{Strength} & \head{Dexterity} & \head{Constitution} & \head{Intelligence} & \head{Wisdom} & \head{Charisma} \\
\textbf{Score}    & 8               & 17               & 14                  & 10                  & 10            & 15 \\
\textbf{Modifier} & \smol{-1}       & \smol{+3}        & \smol{+2}           & \smol{+0}           & \smol{+0}     & \smol{+2} \\
\textbf{Save}     & \smol{-1}       & \smol{+5}        & \smol{+2}           & \smol{+0}           & \smol{+0}     & \smol{+4} \\
\end{tabular}

{\rule{\linewidth}{0.4pt}}

\HPACInitiative{17}{14}{+3}

\begin{center}
\head{Skills}
\end{center}

\newcommand{\E}{\textsuperscript{\dagger}}
\begin{center}
\begin{tabular}{p{0.26\linewidth}@{\hspace{0.8cm}}p{0.26\linewidth}@{\hspace{0.8cm}}p{0.26\linewidth}}
  \skill{Acrobatics}{+4}       & \skill{History}{+1}        & \skill{Performance}{+3} \\
  \skill{Animal Handling}{+1}  & \skill{Insight}{+1}        & \skill*{Persuasion\E}{+6} \\
  \skill*{Arcana}{+2}          & \skill{Intimidation}{+3}   & \skill{Religion}{+1} \\
  \skill{Athletics}{+0}        & \skill{Investigation}{+1}  & \skill{Sleight of Hand}{+4} \\
  \skill{Deception}{+3}        & \skill{Medicine}{+1}       & \skill*{Stealth}{+5} \\
  \skill{Nature}{+1}           & \skill*{Perception\E}{+4}    & \skill*{Survival}{+2} \\
\end{tabular}
\end{center}

{\footnotesize \dagger Expertise}
\newpage


\begin{Card}{Bardic Inspiration}
You can supernaturally inspire others through words, music, or dance. This inspiration is represented by your Bardic Inspiration die, which is a d6.

\textbf{Using Bardic Inspiration.} As a Bonus Action, you can inspire another creature within 60 feet of yourself who can see or hear you. That creature gains one of your Bardic Inspiration dice. A creature can have only one Bardic Inspiration die at a time.

Once within the next hour when the creature fails a D20 Test, the creature can roll the Bardic Inspiration die and add the number rolled to the d20, potentially turning the failure into a success. A Bardic Inspiration die is expended when it's rolled.

\textbf{Number of Uses.} You can confer a Bardic Inspiration die a number of times equal to your Charisma modifier (minimum of once), and you regain all expended uses when you finish a Long Rest.

\textbf{At Higher Levels.} Your Bardic Inspiration die changes when you reach certain Bard levels, as shown in the Bardic Die column of the Bard Features table. The die becomes a d8 at level 5, a d10 at level 10, and a d12 at level 15.
\end{Card}

\begin{Card}[card 1 of 2]{Cartographer's Tools}
Using cartographer's tools, you can create accurate maps to make travel
easier for yourself and those who come after you. These maps can range
from large-scale depictions of mountain ranges to diagrams that show the
layout of a dungeon level.

\textbf{Components.} Cartographer's tools consist of a quill, ink,
parchment, a pair of compasses, calipers, and a ruler.

\textbf{Arcana, History, Religion.} You can use your knowledge of maps
and locations to unearth more detailed information when you use these
skills. For instance, you might spot hidden messages in a map, identify
when the map was made to determine if geographical features have changed
since then, and so forth.

\textbf{Nature.} Your familiarity with physical geography makes it
easier for you to answer questions or solve issues relating to the
terrain around you.
\end{Card}

\begin{Card}[card 2 of 2]{Cartographer's Tools}
Using cartographer's tools, you can create accurate maps to make travel
easier for yourself and those who come after you. These maps can range
from large-scale depictions of mountain ranges to diagrams that show the
layout of a dungeon level.


\textbf{Survival.} Your understanding of geography makes it easier to
find paths to civilization, to predict areas where villages or towns
might be found, and to avoid becoming lost. You have studied so many
maps that common patterns, such as how trade routes evolve and where
settlements arise in relation to geographic locations, are familiar to
you.

\textbf{Craft a Map.} While traveling, you can draw a map as you go in
addition to engaging in other activity.

\begin{tabular}{lc}
\textbf{Activity} & \textbf{DC} \\
Determine a map's age and origin & 10 \\
Estimate direction and distance to a landmark & 15 \\
Discern that a map is fake & 15 \\
Fill in a missing part of a map & 20
\end{tabular}
\end{Card}

\begin{Card}{Harp, Hand Drum, \& Flute}
Proficiency with a musical instrument indicates you are familiar with
the techniques used to play it. You also have knowledge of some songs
commonly performed with that instrument.

\textbf{History.} Your expertise aids you in recalling lore related to
your instrument.

\textbf{Performance.} Your ability to put on a good show is improved
when you incorporate an instrument into your act.

\textbf{Compose a Tune.} As part of a long rest, you can compose a new
tune and lyrics for your instrument. You might use this ability to
impress a noble or spread scandalous rumors with a catchy tune.

\begin{tabular}{lc}
\textbf{Activity} & \textbf{DC} \\
Identify a tune & 10 \\
Improvise a tune & 20
\end{tabular}

\end{Card}

\end{document}
