\documentclass{dnd-deck}
\usepackage{monster}

\begin{document}
\Character{
  pc={Kragor Grimstride},
  summary={Orc Fighter 1/Great Old One Warlock 8},
  player=Jacques,
  levels=9,
  str*=10, dex=14, con*=14, int=8, wis=12, cha=20,
  hp=86, thp=12, ac=21,
  spellcasting=cha}
\SkillProficiencies{Arcana, Insight, Perception, Persuasion}
\LanguageProficiencies{Common, Draconic, Dwarvish, Orc, Undercommon}

\TitleCard[\Summary]{\PC}

\begin{Card}{\PC, \normalsize\Summary}
  \CoreStats{
    Spell={mod=2, note=While holding \textit{Rod of the Pact Keeper $+2$}.},
    SaveCON={note=Advantage on Concentration saves.},
    SaveALL={mod=1, note=While wearing \textit{Cloak of Protection}.},
  }
  \Newpage
  %
  %
  \begin{tabular}{p{0.25\linewidth}p{0.2\linewidth}p{0.1\linewidth}p{0.4\linewidth}}
    \head{Attack}                       & \head{Range}    & \head{Hit}   & \head{Damage/Effect}                 \\
    Battleaxe $\times 2$                & 5 ft (melee)    & $+9$         & $1d8+7$ Slashing, \textit{Topple}    \\
    Rapier $\times 2$                   & 5 ft (melee)    & $+9$         & $1d8+7$ Piercing, \textit{Vex}       \\
    Warhammer $\times 2$                & 5 ft (melee)    & $+9$         & $1d8+7$ Bludgeoning, \textit{Push}   \\
    \textit{Eldritch Blast} $\times 2$  & 120 feet        & $+11$\fmark  & $1d10$ Force
  \end{tabular}
  %
  \ftext{While holding \textit{Rod of the Pact Keeper $+2$}.}
  %
  \ThinRule \par
  \begin{tabular}{p{0.35\linewidth}p{0.30\linewidth}p{0.35\linewidth}}
    \head{Actions}                                 & \head{Bonus Actions}          & \head{Other}                  \\
    Fiendish Vigor: \textit{False Life\fmark}      & Adrenaline Rush\fmarkA        & Lucky\fmarka                  \\
    One with Shadows: \textit{Invisibility\fmark}  & Second Wind\fmarka            & Relentless Endurance\fmarka   \\
                                                   & Pact of the Blade: Bind       & Magical Cunning\fmarka        \\
                                                   & Pact of the Blade: Conjure    & Psychic Spells                \\
                                                   & Awakened Mind                 &                               \\
                                                   & Clairvoyant Combatant\fmarka  &                               \\
  \end{tabular}
  %
  \ftext{At will, self only.}
  \ftext{Limited use.}
  \ftext{At will, self only, while in Dim Light or Darkness.}
  \Newpage
  %
  %
  \sect*{Prepared Spells}
  \begin{PreparedSpells}{p{0.33\linewidth}p{0.33\linewidth}p{0.33\linewidth}}
    \head{Cantrip}                        & \head{2nd Level}                & \head{4th Level}                  \\
    \spell{EldritchBlast}\fmarkA          & \spell{DetectThoughts}          & \spell{Backlash}\fmarka           \\
    \spell{MageHand}                      & \spell{MistyStep}               & \spell{Confusion}                 \\
    \spell{MindSliver}\fmarkB             & \spell{PhantasmalForce}\fmarkb  & \spell{SickeningRadiance}\fmarka  \\
                                          & \spell{Suggestion}\fmarkb       & \spell{ShadowOfMoil}\fmarka       \\
                                          &                                 & \spell{SummonAberration}          \\
    \head{1st Level}                      & \head{3rd Level}                &                                   \\
    \spell{DetectMagic}                   & \spell{Clairvoyance}            &                                   \\
    \spell{DissonantWhispers}\fmarkb      & \spell{Fly}                     &                                   \\
    \spell{Hex}\fmarka\fmarkb             & \spell{HungerOfHadar}\fmarka    &                                   \\
    \spell{TashasHideousLaughter}\fmarkb  & \spell{HypnoticPattern}\fmarkb  &                                   \\
                                          & \spell{SummonFey}               &
  \end{PreparedSpells}
  \ftext{\textbf{Psychic Spells:} You can change the damage type to Psychic.}
  \ftext{\textbf{Psychic Spells:} You can cast this spell without Verbal or Somatic components.}
  \Newpage
  %
  %
  \sect*{Limited Use}
  \begin{ResourceTable}
    \header{Short Rest}                        & \header{Long Rest}                  \\
    \resource{Adrenaline Rush}{\PB}            & \resource{Relentless Endurance}{1}  \\
    \resource{Second Wind\fmark}{2}            & \resource{Luck}{\PB}                \\
    \resource{Pact Slots\fmark}{2}             & \resource{Magical Cunning}{1}       \\
    \resource{Clairvoyant Combatant\fmark}{1}  & \resource{\textit{Hex}}{1}          \\
    &                                          & \resource{\textit{Misty Step}}{1}
  \end{ResourceTable}
  \ftext{You regain one expended use when you finish a Short Rest, and
  you regain all expended uses when you finish a Long Rest.}
  \ftext{All Pact Slots are 4th level.}
  \ftext{You can restore your use of Clairvoyant Combatant by expending a Pact
  Magic spell slot (no action required).}
  \Newpage
  %
  %
  \sect*{Class Features: Warlock}
  \PactMagic
  \MagicalCunning
  \PsychicSpells
  \AwakenedMind
  \ClairvoyantCombatant
  %
  \sect{Class Features: Eldritch Invocations}
  \LessonsOfTheFirstOnes{Skilled}
  \LessonsOfTheFirstOnes{Tough}
  \FiendishVigor
  \PactOfTheBlade
  \ThirstingBlade
  \OneWithShadows
  %
  \sect{Class Features: Fighter}
  \Dueling
  \SecondWind
  \Push{Warhammer}
  \Topple{Battleaxe}
  \Vex{Rapier}
  %
  \sect{Feats}
  \Lucky
  \Tough
  \WarCaster{Charisma}
  %
  %
  \sect*{Species: Orc}
  \SpeciesOrc
\end{Card}

\begin{Card}[Rare Item]{Rod of the Pact Keeper $+2$}
  While holding this rod, you gain a bonus to spell attack rolls and to the
  saving throw DCs of your Warlock spells. The bonus is determined by the rod's
  rarity.

  In addition, you can regain one spell slot as a Magic action while holding the
  rod. You can't use this property again until you finish a Long Rest.

  \textit{Requires Attunment by a Warlock.}
\end{Card}

\begin{Card}[Uncommon Item]{Cloak of Protection}
  You gain a +1 bonus to Armor Class and saving throws while you wear this
  cloak.

  \textit{Requires Attunment.}
\end{Card}

\begin{Card}[Uncommon Armor]{Mithral Splint}
  This armor is made of narrow vertical strips of Mithral riveted to a backing
  of leather that is worn over cloth padding. Flexible Mithral chain mail
  protects the joints.

  Mithral is a light, flexible metal. Armor made of this substance can be worn
  under normal clothes. If the armor normally imposes Disadvantage on Dexterity
  (Stealth) checks or has a Strength requirement, the mithral version of the
  armor doesn't.

  \textbf{Armor Class:} 17.
\end{Card}

\SpellCards

\MonsterAbberantSpirit
\MonsterFeySpirit

\Placard

\end{document}
