\input{include.tex}

\begin{document}
\pagestyle{empty}

\begin{Spell}[
  level=Cantrip,
  time=1 Action,
  range=120 ft.,
  components={V, S},
  duration=Instantaneous,
  school=Evocation,
  attack=Ranged,
  effect=Force
]{Eldritch Blast}
You hurl a beam of crackling energy. Make a ranged spell attack against one creature or object in range. On a hit, the target takes 1d10 Force damage.

\textbf{Cantrip Upgrade.} The spell creates two beams at level 5, three beams at level 11, and four beams at level 17. You can direct the beams at the same target or at different ones. Make a separate attack roll for each beam.
\end{Spell}


\begin{Spell}[
  level=Cantrip,
  time=1 Action,
  range=30 ft.,
  components={V, S},
  duration=1 Minute,
  school=Conjuration,
  attack=None,
  effect=Utility
]{Mage Hand}
A spectral, floating hand appears at a point you choose within range. The hand lasts for the duration. The hand vanishes if it is ever more than 30 feet away from you or if you cast this spell again.

When you cast the spell, you can use the hand to manipulate an object, open an unlocked door or container, stow or retrieve an item from an open container, or pour the contents out of a vial.

As a Magic action on your later turns, you can control the hand thus again. As part of that action, you can move the hand up to 30 feet.

The hand can't attack, activate magic items, or carry more than 10 pounds.
\end{Spell}

\begin{Spell}[
  level=1st,
  time=1 Bonus Action,
  range=Self,
  components={V, S, M*},
  duration=1 Hour,
  school=Abjuration,
  attack=None,
  effect=Cold
]{Armor of Agathys}
Protective magical frost surrounds you. You gain 5 Temporary Hit Points. If a creature hits you with a melee attack roll before the spell ends, the creature takes 5 Cold damage. The spell ends early if you have no Temporary Hit Points.

\textbf{Using a Higher-Level Spell Slot.} The Temporary Hit Points and the Cold damage both increase by 5 for each spell slot level above 1.

* - (a shard of blue glass)

\end{Spell}

\begin{Spell}[
  tags=Concentration,
  level=1st,
  time=1 Bonus Action,
  range=90 ft.,
  components={V, S, M*},
  duration=1 Hour,
  school=Enchantment,
  attack=None,
  effect=Necrotic
]{Hex}
You place a curse on a creature that you can see within range. Until the spell ends, you deal an extra 1d6 Necrotic damage to the target whenever you hit it with an attack roll. Also, choose one ability when you cast the spell. The target has Disadvantage on ability checks made with the chosen ability.

If the target drops to 0 Hit Points before this spell ends, you can take a Bonus Action on a later turn to curse a new creature.

\textbf{Using a Higher-Level Spell Slot.} Your \textit{Concentration} can last longer with a spell slot of level 2 (up to 4 hours), 3–4 (up to 8 hours), or 5+ (24 hours).

* - (the petrified eye of a newt)

\end{Spell}

\begin{Spell}[
  tags={Concentration, Ritual},
  level=1st,
  time=1 Action,
  range=Self (30 ft.),
  components={V, S},
  duration=10 Minutes,
  school=Divination,
  attack=None,
  effect=Detection
]{Detect Magic}
For the duration, you sense the presence of magical effects within 30 feet of yourself. If you sense such effects, you can take the Magic action to see a faint aura around any visible creature or object in the area that bears the magic, and if an effect was created by a spell, you learn the spell's school of magic.

The spell is blocked by 1 foot of stone, dirt, or wood; 1 inch of metal; or a thin sheet of lead.
\end{Spell}
\end{document}
