\input{include.tex}
\begin{document}
\pagestyle{empty}

\CardTitle{Charm Person}
\begin{Spell}{1st}{1 Action}{30 ft}{V, S}{1 Hour}{Enchantment}{WIS Save}{Charmed}

One Humanoid you can see within range makes a Wisdom saving throw. It does so with Advantage if you or your allies are fighting it. On a failed save, the target has the Charmed condition until the spell ends or until you or your allies damage it. The Charmed creature is Friendly to you. When the spell ends, the target knows it was Charmed by you.

\textbf{Using a Higher-Level Spell Slot.} You can target one additional creature for each spell slot level above 1.

\end{Spell}

\CardTitle{Comprehend Languages}
\begin{Spell}{1st}{1 Action}{Self}{V, S, M*}{1 Hour}{Divination}{None}{Social}

For the duration, you understand the literal meaning of any language that you hear or see signed. You also understand any written language that you see, but you must be touching the surface on which the words are written. It takes about 1 minute to read one page of text. This spell doesn’t decode symbols or secret messages.

* - (a pinch of soot and salt)
\end{Spell}


\CardTitle{Cure Wounds}
\begin{Spell}{1st}{1 Action}{Touch}{V, S}{Instantaneous}{Abjuration}{None}{Healing}
A creature you touch regains a number of Hit Points equal to 2d8 plus your spellcasting ability modifier.

\textbf{Using a Higher-Level Spell Slot.} The healing increases by 2d8 for each spell slot level above 1.
\end{Spell}

\CardTitle{Disguise Self}
\begin{Spell}{1st}{1 Action}{Self}{V, S}{1 Hour}{Illusion}{None}{Shapechanging}

You make yourself—including your clothing, armor, weapons, and other belongings on your person—look different until the spell ends. You can seem 1 foot shorter or taller and can appear heavier or lighter. You must adopt a form that has the same basic arrangement of limbs as you have. Otherwise, the extent of the illusion is up to you.

The changes wrought by this spell fail to hold up to physical inspection. For example, if you use this spell to add a hat to your outfit, objects pass through the hat, and anyone who touches it would feel nothing.

To discern that you are disguised, a creature must take the Study action to inspect your appearance and succeed on an Intelligence (Investigation) check against your spell save DC.
\end{Spell}

\CardTitle{Feather Fall}
\begin{Spell}{1st}{1 Reaction*}{60 ft.}{V, M**}{1 Minute}{Transmutation}{None}{Exploration}

Choose up to five falling creatures within range. A falling creature's rate of descent slows to 60 feet per round until the spell ends. If a creature lands before the spell ends, the creature takes no damage from the fall, and the spell ends for that creature.

* - which you take when you or a creature you can see within 60 feet of you falls

** - (a small feather or piece of down)
\end{Spell}

\CardTitle{Heroism}
\begin{Spell}{1st}{1 Action}{Touch}{V, S}{Concentration 1 Minute}{Enchantment}{None}{Frightened}

A willing creature you touch is imbued with bravery. Until the spell ends, the creature is immune to the Frightened condition and gains Temporary Hit Points equal to your spellcasting ability modifier at the start of each of its turns.

\textbf{Using a Higher-Level Spell Slot.} You can target one additional creature for each spell slot level above 1.
\end{Spell}


\CardTitle[Concentration]{Silent Image}
\begin{Spell}{1st}{1 Action}{60 ft. (15 ft. cube)}{V, S, M*}{10 Minutes}{Illusion}{None}{Control}

You create the image of an object, a creature, or some other visible phenomenon that is no larger than a 15-foot Cube. The image appears at a spot within range and lasts for the duration. The image is purely visual; it isn't accompanied by sound, smell, or other sensory effects. As a Magic action, you can cause the image to move to any spot within range. As the image changes location, you can alter its appearance so that its movements appear natural for the image. For example, if you create an image of a creature and move it, you can alter the image so that it appears to be walking.
Physical interaction with the image reveals it to be an illusion, since things can pass through it. A creature that takes a Study action to examine the image can determine that it is an illusion with a successful Intelligence (Investigation) check against your spell save DC. If a creature discerns the illusion for what it is, the creature can see through the image.

* - (a bit of fleece)
\end{Spell}

\CardTitle[Concentration]{Sleep}
\begin{Spell}{1st}{1 Action}{60 ft. (5 ft. sphere)}{V, S, M*}{1 Minute}{Enchantment}{WIS Save}{Incapacitated}

Each creature of your choice in a 5-foot-radius Sphere centered on a point within range must succeed on a Wisdom saving throw or have the Incapacitated condition until the end of its next turn, at which point it must repeat the save. If the target fails the second save, the target has the Unconscious condition for the duration. The spell ends on a target if it takes damage or someone within 5 feet of it takes an action to shake it out of the spell's effect.

Creatures that don't sleep, such as elves, or that have Immunity to the Exhaustion condition automatically succeed on saves against this spell.

* - (a pinch of sand or rose petals)
\end{Spell}

\CardTitle{Tasha's Hideous Laughter}
\begin{Spell}{1st}{1 Action}{30 ft.}{V, S, M*}{Concentration 1 Minute}{Enchantment}{WIS Save}{Prone}

One creature of your choice that you can see within range makes a Wisdom saving throw. On a failed save, it has the Prone and Incapacitated conditions for the duration. During that time, it laughs uncontrollably if it's capable of laughter, and it can't end the Prone condition on itself.

At the end of each of its turns and each time it takes damage, it makes another Wisdom saving throw. The target has Advantage on the save if the save is triggered by damage. On a successful save, the spell ends.

\textbf{Using a Higher-Level Spell Slot.} You can target one additional creature for each spell slot level above 1.

* - (a tart and a feather)
\end{Spell}

\CardTitle{Thunderwave}
\begin{Spell}{1st}{1 Action}{Self (15 ft.)}{V, S}{Instantaneous}{Evocation}{CON Save}{Thunder}

You unleash a wave of thunderous energy. Each creature in a 15-foot Cube originating from you makes a Constitution saving throw. On a failed save, a creature takes 2d8 Thunder damage and is pushed 10 feet away from you. On a successful save, a creature takes half as much damage only.

In addition, unsecured objects that are entirely within the Cube are pushed 10 feet away from you, and a thunderous boom is audible within 300 feet.

\textbf{Using a Higher-Level Spell Slot.} The damage increases by 1d8 for each spell slot level above 1.
\end{Spell}

\CardTitle{Goodberry}
\begin{Spell}{1st}{1 Action}{Self}{V, S, M*}{24 Hours}{Conjuration}{None}{Healing}

Ten berries appear in your hand and are infused with magic for the duration. A creature can take a Bonus Action to eat one berry. Eating a berry restores 1 Hit Point, and the berry provides enough nourishment to sustain a creature for one day.

Uneaten berries disappear when the spell ends.

* - (a sprig of mistletoe)
\end{Spell}

\end{document}
