\input{include.tex}
\begin{document}
\pagestyle{empty}

\CardTitle{Produce Flame}

\begin{Spell}{Cantrip}{1 Bonus Action}{Self}{V, S}{10 Minutes}{Conjuration}{Ranged}{Fire}

A flickering flame appears in your hand and remains there for the duration. While there, the flame emits no heat and ignites nothing, and it sheds Bright Light in a 20-foot radius and Dim Light for an additional 20 feet. The spell ends if you cast it again.

Until the spell ends, you can take a Magic action to hurl fire at a creature or an object within 60 feet of you. Make a ranged spell attack. On a hit, the target takes 1d8 Fire damage.

\textbf{Cantrip Upgrade.} The damage increases by 1d8 when you reach levels 5 (2d8), 11 (3d8), and 17 (4d8).

\end{Spell}

\CardTitle{Shillelagh}

\begin{Spell}{Cantrip}{1 Bonus Action}{Self}{V, S, M*}{1 Minute}{Transmutation}{Melee}{Bludgeoning}

A Club or Quarterstaff you are holding is imbued with nature's power. For the duration, you can use your spellcasting ability instead of Strength for the attack and damage rolls of melee attacks using that weapon, and the weapon's damage die becomes a d8. If the attack deals damage, it can be Force damage or the weapon's normal damage type (your choice).

The spell ends early if you cast it again or if you let go of the weapon.

\textbf{Cantrip Upgrade.} The damage die changes when you reach levels 5 (d10), 11 (d12), and 17 (2d6).

* - (mistletoe)
\end{Spell}

\CardTitle{Cure Wounds}

\begin{Spell}{1st}{1 Action}{Touch}{V, S}{Instantaneous}{Abjuration}{None}{Healing}

A creature you touch regains a number of Hit Points equal to 2d8 plus your spellcasting ability modifier.

\textbf{Using a Higher-Level Spell Slot.} The healing increases by 2d8 for each spell slot level above 1.

\end{Spell}

\CardTitle[Concentration, Ritual]{Detect Poison and Disease}

\begin{Spell}{1st}{1 Action}{Self (30 ft.)}{V, S, M*}{10 Minutes}{Divination}{None}{Detection}

For the duration, you sense the location of poisons, poisonous or venomous creatures, and magical contagions within 30 feet of yourself. You sense the kind of poison, creature, or contagion in each case.

The spell is blocked by 1 foot of stone, dirt, or wood; 1 inch of metal; or a thin sheet of lead.

* - (a yew leaf)

\end{Spell}

\CardTitle[Concentration]{Entangle}

\begin{Spell}{1st}{1 Action}{90 ft. (20 ft.)}{V, S}{1 Minute}{Conjuration}{STR Save}{Restrained}

Grasping plants sprout from the ground in a 20-foot square within range. For the duration, these plants turn the ground in the area into Difficult Terrain. They disappear when the spell ends.

Each creature (other than you) in the area when you cast the spell must succeed on a Strength saving throw or have the Restrained condition until the spell ends. A Restrained creature can take an action to make a Strength (Athletics) check against your spell save DC. On a success, it frees itself from the grasping plants and is no longer Restrained by them.

\end{Spell}

\CardTitle{Thunderwave}

\begin{Spell}{1st}{1 Action}{Self (15 ft.)}{V, S}{Instantaneous}{Evocation}{CON Save}{Thunder}

You unleash a wave of thunderous energy. Each creature in a 15-foot Cube originating from you makes a Constitution saving throw. On a failed save, a creature takes 2d8 Thunder damage and is pushed 10 feet away from you. On a successful save, a creature takes half as much damage only.

In addition, unsecured objects that are entirely within the Cube are pushed 10 feet away from you, and a thunderous boom is audible within 300 feet.

\textbf{Using a Higher-Level Spell Slot.} The damage increases by 1d8 for each spell slot level above 1.

\end{Spell}

\CardTitle{Primal Savagery}
\begin{Spell}{Cantrip}{1 Action}{5 ft.}{S}{Instantaneous}{Transmutation}{Melee}{Acid}
You channel primal magic to cause your teeth or fingernails to sharpen, ready to deliver a corrosive attack. Make a melee spell attack against one creature within 5 feet of you. On a hit, the target takes 1d10 acid damage. After you make the attack, your teeth or fingernails return to normal.

\textbf{Cantrip Upgrade.} The spell's damage increases by 1d10 when you reach 5th level (2d10), 11th level (3d10), and 17th level (4d10).
\end{Spell}

\CardTitle{Speak with Animals}

\begin{Spell}{1st}{1 Action}{Self}{V,S}{10 Minutes}{Divination}{None}{Communication}

For the duration, you can comprehend and verbally communicate with Beasts, and you can use any of the Influence action's skill options with them.

Most Beasts have little to say about topics that don't pertain to survival or companionship, but at minimum, a Beast can give you information about nearby locations and monsters, including whatever it has perceived within the past day.

\end{Spell}
\end{document}
