\begin{Spell}[
  tags=Concentration,
  level={3rd},
  time={1 action},
  range={120 ft/20 ft cube},
  components={V, S, M},
  duration={10 minutes},
  school={Illusion},
  attack={INT Check},
  effect={Control}
]{Major Image}
You create the image of an object, a creature, or some other visible phenomenon that is no larger than a 20-foot cube. The image appears at a spot that you can see within range and lasts for the duration. It seems real, including sounds, smells, and temperature appropriate to the thing depicted, but it can't deal damage or cause conditions.

If you are within range of the illusion, you can take a Magic action to cause the image to move to any other spot within range. As the image changes location, you can alter its appearance so that its movements appear natural for the image. You can also cause the illusion to make different sounds at different times, even making it carry on a conversation.

\hfill \textit{\footnotesize continues}
\newpage
\CardTitle[continued]{Major Image}

Physical interaction with the image reveals it to be an illusion, as things can pass through it. A creature that takes a Study action to examine the image can determine that it is an illusion with a successful Intelligence (Investigation) check against your spell save DC. If a creature discerns the illusion for what it is, the creature can see through the image, and its other sensory qualities become faint to the creature.

\textbf{Using a Higher-Level Spell Slot.} The spell lasts until dispelled, without requiring Concentration, if cast with a 4th-level or higher spell slot.

\begin{components}
V & \textit{Sensus decipio (SEN-soos day-KEE-pee-oh)} \\
M & a bit of fleece
\end{components}
\end{Spell}


